---
title: 'Basic Inferential Data Analysis'
author: Bo Liu
date: March 27, 2017
output:
  pdf_document: default
---
## Overview
This report explores the growth of the odontoblast, the cell responsible for tooth growth, of the incisor teeth as a criterion of vitamin C intake of a guinea pig. In this study, 60 guinea pigs each received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, orange juice or ascorbic acid.

### Load the ToothGrowth data and perform some basic exploratory data analyses
```{r}
library(ggplot2);library(datasets);library(Hmisc)
data("ToothGrowth")
head(ToothGrowth)
smry <- stat_summary(geom="crossbar", width=0.3, fun.data="mean_cl_boot") 
meanline <- stat_summary(geom="line",fun="mean_se")
qplot(dose, len, data=ToothGrowth, colour=supp, xlab="vitamin C Dose(mg/day)", ylab="Tooth Length") + smry + meanline
```

### Provide a basic summary of the data.
From this figure, we can see the trend of len when supp and dose change. The len increasing as dose changing from 0.5 to 2 or supp status turn from VC to OJ. 
We can illustrate our hyperthesis

### Use confidence intervals to compare tooth growth by supp and dose.
First, calculate mu and sigma.
```{r}
mu<-mean(ToothGrowth$len)
sigma<-var(ToothGrowth$len)
mu
sigma
```
Second, calculate the confidence intervals, say 95% intervals.
```{r}
n <- length(ToothGrowth$len)
con_int<-mu + c(-1,1)*2*sigma/sqrt(n)
con_int
```
We see that confidence intervals is [3.705594, 33.921073].   
Third, let's calculate the mean by supp and dose.
```{r}
unique(ToothGrowth$supp)
meansuppvc<-mean(ToothGrowth$len[ToothGrowth$supp=='VC'])
meansuppoj<-mean(ToothGrowth$len[ToothGrowth$supp=='OJ'])
meansuppvc
meansuppoj
unique(ToothGrowth$dose)
meandose05<-mean(ToothGrowth$len[ToothGrowth$dose==.5])
meandose10<-mean(ToothGrowth$len[ToothGrowth$dose==1.0])
meandose20<-mean(ToothGrowth$len[ToothGrowth$dose==2.0])
meandose05
meandose10
meandose20
```
Finally, compare those mean values to confidence intervals.
```{r}
con_int-meansuppvc
con_int-meansuppoj
con_int-meandose05
con_int-meandose10
con_int-meandose20
```
If the result values were both negtive or positive, means that the mean value is not in the confidence intervals. Otherwise, the mean value is in the range of confidence intervals.

### Conclusions.
Since all the mean values are in the confidence intervals, we can conclude that all those results are believable.
